Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-08-31 paper_comparison/paper_comparison/paper_comparison.Rmd
paper structure

```{r}
library(tidyverse)
library(visage)

@@

> *"Since all models are wrong the scientist must be alert to what is importantly wrong [@box1976science]."*

@@

## Diagnostic plots

@@

## Visual inference

However, unlike hypothesis testing built upon rigorous statistical procedures, reading diagnostic plots relies on graphical perception - human’s ability to interpret and decode the information embedded in the graph [@cleveland_graphical_1984], which is to some extent subjective and indecisive. Further, visual discovery suffers from its unsecured and unconfirmed nature where the degree of the presence of the visual features typically can not be measured quantitatively and objectively, which may lead to over or under-interpretations of the data. One such example is finding an over-interpretation of the separation between gene groups in a two-dimensional projection from a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups and separation is not an uncommon occurrence [@roy_chowdhury_using_2015].

@@

@@

# Results

## Data preprocessing

@@

>>>>

```{r}
library(tidyverse)
# remotes::install_github("TengMCing/visage")
library(visage)

@@

> *"Since all models are wrong the scientist must be alert to what is importantly wrong."*  [@box1976science]

@@

## Departures from good residual plots

@@

## Conventionally testing for departures

Explain the tests you are showing later

- RESET
- BP
- SW

and show the results for the residual plots displayed in previous section

Briefly mention any others

## Visual testing for departures

- Very briefly explain what a lineup test is
- Lineup (maybe using your previous residual plot for nonlinearity)
- $p$-value calulcation, briefly, including how multiple selections are handled
- power calculation, briefly, including how multiple selections are handled

However, unlike hypothesis testing built upon rigorous statistical procedures, reading diagnostic plots relies on graphical perception - human's ability to interpret and decode the information embedded in the graph [@cleveland_graphical_1984], which is to some extent subjective and indecisive. Further, visual discovery suffers from its unsecured and unconfirmed nature where the degree of the presence of the visual features typically can not be measured quantitatively and objectively, which may lead to over or under-interpretations of the data. One such example is finding an over-interpretation of the separation between gene groups in a two-dimensional projection from a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups and separation is not an uncommon occurrence [@roy_chowdhury_using_2015].

@@

## Motivation and overview

## Simulating departures

### Nonlinearity

### Heteroskedasticity

## Experimental setup

### Factors

- Treatments for nonlinearity experiment (plots summarising levels)
- Treatments for heteroskedasticity experiment (plots summarising levels)

### Assigning subjects

### Collecting results

software/technical

## Computing power curves

@@

# Analysis and results

## Data overview

How many people? How many lineups?

@@

##

## Nonlinearity

- Power curve overall
- Four lineups also shown, selected from ones close to the visual power curve from the uniform treatment
- Compare visual power against different factors

- Power curve overall
- Four lineups also shown, selected from ones close to the visual power curve from the uniform treatment
- Compare visual power against different factors

### 2022-08-31 paper_comparison/paper_comparison/paper_comparison.tex
paper structure

\begin{quote}
\emph{``Since all models are wrong the scientist must be alert to what
is importantly wrong \citep{box1976science}.''}
\end{quote}

@@

\hypertarget{diagnostic-plots}{%
\subsection{Diagnostic plots}\label{diagnostic-plots}}

@@

\hypertarget{visual-inference}{%
\subsection{Visual inference}\label{visual-inference}}

@@

@@

\hypertarget{heteroskedasticity}{%
\subsection{Heteroskedasticity}\label{heteroskedasticity}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{data-preprocessing}{%
\subsection{Data preprocessing}\label{data-preprocessing}}

@@

>>>>

\begin{quote}
\emph{``Since all models are wrong the scientist must be alert to what
is importantly wrong.''} \citep{box1976science}
\end{quote}

@@

\hypertarget{departures-from-good-residual-plots}{%
\subsection{Departures from good residual
plots}\label{departures-from-good-residual-plots}}

@@

\hypertarget{conventionally-testing-for-departures}{%
\subsection{Conventionally testing for
departures}\label{conventionally-testing-for-departures}}

Explain the tests you are showing later

\begin{itemize}
\tightlist
\item
  RESET
\item
  BP
\item
  SW
\end{itemize}

and show the results for the residual plots displayed in previous
section

Briefly mention any others

\hypertarget{visual-testing-for-departures}{%
\subsection{Visual testing for
departures}\label{visual-testing-for-departures}}

\begin{itemize}
\tightlist
\item
  Very briefly explain what a lineup test is
\item
  Lineup (maybe using your previous residual plot for nonlinearity)
\item
  \(p\)-value calulcation, briefly, including how multiple selections
  are handled
\item
  power calculation, briefly, including how multiple selections are
  handled
\end{itemize}

@@

\hypertarget{motivation-and-overview}{%
\subsection{Motivation and overview}\label{motivation-and-overview}}

\hypertarget{simulating-departures}{%
\subsection{Simulating departures}\label{simulating-departures}}

\hypertarget{nonlinearity}{%
\subsubsection{Nonlinearity}\label{nonlinearity}}

\hypertarget{heteroskedasticity}{%
\subsubsection{Heteroskedasticity}\label{heteroskedasticity}}

\hypertarget{experimental-setup}{%
\subsection{Experimental setup}\label{experimental-setup}}

\hypertarget{factors}{%
\subsubsection{Factors}\label{factors}}

\begin{itemize}
\tightlist
\item
  Treatments for nonlinearity experiment (plots summarising levels)
\item
  Treatments for heteroskedasticity experiment (plots summarising
  levels)
\end{itemize}

\hypertarget{assigning-subjects}{%
\subsubsection{Assigning subjects}\label{assigning-subjects}}

\hypertarget{collecting-results}{%
\subsubsection{Collecting results}\label{collecting-results}}

software/technical

\hypertarget{computing-power-curves}{%
\subsection{Computing power curves}\label{computing-power-curves}}

@@

\hypertarget{heteroskedasticity-1}{%
\subsection{Heteroskedasticity}\label{heteroskedasticity-1}}

@@

\hypertarget{analysis-and-results}{%
\section{Analysis and results}\label{analysis-and-results}}

\hypertarget{data-overview}{%
\subsection{Data overview}\label{data-overview}}

How many people? How many lineups?

@@

\hypertarget{section}{%
\subsection{}\label{section}}

\hypertarget{nonlinearity-1}{%
\subsection{Nonlinearity}\label{nonlinearity-1}}

\begin{itemize}
\tightlist
\item
  Power curve overall
\item
  Four lineups also shown, selected from ones close to the visual power
  curve from the uniform treatment
\item
  Compare visual power against different factors
\end{itemize}

\hypertarget{heteroskedasticity-2}{%
\subsection{Heteroskedasticity}\label{heteroskedasticity-2}}

\begin{itemize}
\tightlist
\item
  Power curve overall
\item
  Four lineups also shown, selected from ones close to the visual power
  curve from the uniform treatment
\item
  Compare visual power against different factors
\end{itemize}
